### 2020-07-19 manuscript/explorations/phylobayes_explorations.rmd
makes nCAT60, nCAT100, and cat plots

  allocation_counts = table(pb@allocation)

  # Building on https://www.statmethods.net/advstats/mds.html
  d = dist( pb@frequencies )
  fit = cmdscale(d,eig=TRUE, k=2)

  categories = tibble(
    index = allocation_counts %>% names() %>% as.numeric(),
    count = c(allocation_counts),
    x = fit$points[,1],
    y = fit$points[,2]
  )

  gg_mds = 
  categories %>% 
    ggplot() +
    geom_point(aes(x=x, y=y, size=count) ) +
    ggtitle("MDS plot of rate categories") +
    theme_classic()

>>>>

  allocation_counts = table(pb@allocation)
  index = allocation_counts %>% names() %>% as.numeric()

  if( ! all( index %in% rownames(pb@frequencies) ) ){
    stop("Allocations are outside available category range")
  }

  # Consider only the subset of frequencies that are allocated
  frequencies = pb@frequencies[ match(index , rownames(pb@frequencies) ), ]

  # Building on https://www.statmethods.net/advstats/mds.html
  d = dist( frequencies )
  fit = cmdscale(d,eig=TRUE, k=2)

  categories = tibble(
    index = index,
    count = c(allocation_counts),
    x = fit$points[,1],
    y = fit$points[,2]
  )

  gg_mds = 
  categories %>% 
    ggplot() +
    geom_point(aes(x=x, y=y, size=count), alpha=0.4 ) +
    ggtitle("MDS plot of rate categories") +
    theme_classic()
